Poseidon Adventure

### 2019-05-21 docs/index.Rmd
add wt age to index
update index

## Weight at age: by output age class, how to get to true age basis?

@@

>>>>

### Weight at age: by output age class, how to get to true age basis?

@@

Work in progress on interpolating weight at age in InterpolateWeightAtAge.Rmd

Work TBD applying `calc_stage2age` and `calc_Z` to get true ages

### Testing a full workflow through fisheries (sardine, agecl = true age)

<a href="https://sgaichas.github.io/poseidon-dev/Atlantisom2SSworkflowtest.html" target="_blank">Try for true datasets new CC model with climate - May 21, 2019</a>

Fishery catch problem, older codebase has a bug in output. Test with NOBA...
